Filling in the Gaps: Using Consumer Products to Replace Missing Pollution Data

### 2022-03-07 paper/15min-presentation/15min-presentation.tex

%---------------------------------------------------------
%Results: Sample EPA Sites
\begin{frame}
\frametitle{Results: Sample EPA Sites}
\includegraphics[width=\textwidth]{}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Results: Fresno
\begin{frame}
\frametitle{Results: Fresno}
\begin{table}[]
\caption{Design Value Comparison for Fresno, CA. (98\% CI Bounds)}
\label{tab:fresno_dvs}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}l|lll|lll@{}}
Year-Quarter & \begin{tabular}[c]{@{}l@{}}Annual DV\\ Difference\end{tabular} & \begin{tabular}[c]{@{}l@{}}Upper \\ Bound\end{tabular} & \begin{tabular}[c]{@{}l@{}}Lower\\ Bound\end{tabular} & \begin{tabular}[c]{@{}l@{}}Hour DV \\ Difference\end{tabular} & \begin{tabular}[c]{@{}l@{}}Upper \\ Bound\end{tabular} & \begin{tabular}[c]{@{}l@{}}Lower \\ Bound\end{tabular} \\ \midrule
2018-4 & Invalid DV &  &  & Invalid DV &  &  \\
2019-1 & -0.005 & 0.133 & -0.143 & 0.000 & 0.252 & 0.000 \\
2019-2 & -0.003 & 0.141 & -0.147 & 0.000 & 0.252 & 0.000 \\
2019-3 & 0.015 & 0.170 & -0.139 & 0.058 & 2.202 & 0.000 \\
2019-4 & 0.002 & 0.190 & -0.185 & 0.000 & 1.460 & -0.024 \\
2020-1 & -0.012 & 0.182 & -0.207 & 0.000 & 0.335 & 0.000 \\
2020-2 & -0.010 & 0.191 & -0.211 & 0.000 & 0.376 & 0.000 \\
2020-3 & 0.679 & 0.954 & 0.403 & 8.718 & 11.704 & 8.556 \\
2020-4 & 0.647 & 1.006 & 0.288 & 5.979 & 8.281 & 5.851 \\
2021-1 & 0.564 & 1.036 & 0.091 & 3.007 & 4.184 & 2.903 \\
2021-2 & 0.533 & 1.024 & 0.042 & 3.007 & 4.225 & 2.903 \\
2021-3 & 0.630 & 1.129 & 0.132 & 7.607 & 10.557 & 7.444
\end{tabular}%
}
\end{table}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Conclusions & Discussion
\begin{frame}
\frametitle{Conclusions \& Discussion}
\end{frame}
%---------------------------------------------------------

@@

%---------------------------------------------------------
%Extra Tables
\begin{frame}
\frametitle{Table: }
\end{frame}
%---------------------------------------------------------

>>>>

%---------------------------------------------------------
%Results: Sample EPA Sites
\begin{frame}
\frametitle{Results for Daily Design Value: Sample EPA Sites}
\includegraphics[width=\textwidth]{output/figures/final_results/DV_plot_all_test_sites.png}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Results: Fresno
\begin{frame}
\frametitle{Results for Daily Design Value: Fresno}

\includegraphics[width=\textwidth]{output/figures/final_results/DV_plot_site_019-0500.png}

%---------------------------------------------------------
%Results: Sample EPA Sites
\begin{frame}
\frametitle{Results for 24-hour Design Value: Sample EPA Sites}
\includegraphics[width=\textwidth]{output/figures/final_results/DV}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Results: Fresno
\begin{frame}
\frametitle{Results for 24-hour Design Value: Fresno}

\includegraphics[width=\textwidth]{output/figures/final_results/DV_plot_site_019-0500.png}

%---------------------------------------------------------
%Conclusions & Discussion
\begin{frame}
\frametitle{Conclusions \& Discussion}
\begin{enumerate}
    \item Most sites tested show little evidence of bias from missing data, but some have large, meaningful bias
\end{enumerate}
\end{frame}
%---------------------------------------------------------

@@

%---------------------------------------------------------
% Fresno Site Data
\begin{frame}
\frametitle{Fresno Site Data}

\hspace{5em}
\includegraphics[width=0.8\textwidth]{pics/appendix/site_plots/site-019-0500_epa-pa-hourly-plot.png}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Extra Tables
\begin{frame}
\frametitle{Table: Fresno, California}

\begin{table}[]
\caption{Design Value Comparison for Fresno, CA. (98\% CI Bounds)}
\label{tab:fresno_dvs}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}l|lll|lll@{}}
Year-Quarter & \begin{tabular}[c]{@{}l@{}}Annual DV\\ Difference\end{tabular} & \begin{tabular}[c]{@{}l@{}}Upper \\ Bound\end{tabular} & \begin{tabular}[c]{@{}l@{}}Lower\\ Bound\end{tabular} & \begin{tabular}[c]{@{}l@{}}Hour DV \\ Difference\end{tabular} & \begin{tabular}[c]{@{}l@{}}Upper \\ Bound\end{tabular} & \begin{tabular}[c]{@{}l@{}}Lower \\ Bound\end{tabular} \\ \midrule
2018-4 & Invalid DV &  &  & Invalid DV &  &  \\
2019-1 & -0.005 & 0.133 & -0.143 & 0.000 & 0.252 & 0.000 \\
2019-2 & -0.003 & 0.141 & -0.147 & 0.000 & 0.252 & 0.000 \\
2019-3 & 0.015 & 0.170 & -0.139 & 0.058 & 2.202 & 0.000 \\
2019-4 & 0.002 & 0.190 & -0.185 & 0.000 & 1.460 & -0.024 \\
2020-1 & -0.012 & 0.182 & -0.207 & 0.000 & 0.335 & 0.000 \\
2020-2 & -0.010 & 0.191 & -0.211 & 0.000 & 0.376 & 0.000 \\
2020-3 & 0.679 & 0.954 & 0.403 & 8.718 & 11.704 & 8.556 \\
2020-4 & 0.647 & 1.006 & 0.288 & 5.979 & 8.281 & 5.851 \\
2021-1 & 0.564 & 1.036 & 0.091 & 3.007 & 4.184 & 2.903 \\
2021-2 & 0.533 & 1.024 & 0.042 & 3.007 & 4.225 & 2.903 \\
2021-3 & 0.630 & 1.129 & 0.132 & 7.607 & 10.557 & 7.444
\end{tabular}%
}
\end{table}
\end{frame}
%---------------------------------------------------------
